Composable Concurrency Models

### 2016-10-10 paper/paper.tex
Fixed references

\documentclass{sig-alternate}
\usepackage{biblatex}
\usepackage{listings}

@@

% space is limited:
\AtEveryBibitem{\clearfield{doi}}
\AtEveryBibitem{\clearfield{isbn}}
\AtEveryBibitem{\clearfield{note}}
\AtEveryBibitem{\clearfield{url}}

@@

\begin{lstlisting}[language=C]
  bool swap(int* v, int old, int new) {
    if (*v != old) {
      return false;
    }

    *v = new;
    return true;
  }
\end{lstlisting}

@@

\begin{lstlisting}
  atomic (index > 0) {
    index--;
    return buffer[index];
  }
\end{lstlisting}

@@

\begin{lstlisting}
  v = TVar.new(50)

  Concurrent::atomically do
    v.value += 50
  end
\end{lstlisting}

@@

\begin{lstlisting}
  var read = new Promise((resolve) => {
    fs.readdir('.', resolve);
  });

  var count = (files) => {
    return new Promise((resolve) {
      resolve(files.length);
    });
  };

  var print = console.log;

  read.then(count).then(print);
\end{lstlisting}

@@

\section{Acknowledgments}

@@

\section{References}

\nocite{*}

\printbibliography[heading=none]

>>>>

\documentclass{sig-alternate}
\usepackage[backend=bibtex,style=numeric-comp]{biblatex}

@@

\AtEveryBibitem{\clearfield{note}}

@@

@@

@@

@@

@@

\section*{Acknowledgments}

@@

\printbibliography{}
